<<<<<<< HEAD
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-----------------------------------------------------------------------------
\vspace{-3mm}
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\vspace{-1mm}
\begin{cventries}

%---------------------------------------------------------
\cventry
{\textbf{Core Competencies \& Accomplishments}} % Job title
{\href{https://www.zluri.com/}{Zluri, Bangalore}} % Organization
{Apr. 2022 - Present} % Date(s)
{} % Location
{\begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{Document Intelligence (NLP):} Architected an end-to-end contract extraction pipeline using \textbf{TensorFlow Transform} and \textbf{Keras} to build a custom Transformer-based NER model. This system automatically identifies renewal dates and fiscal obligations in unstructured PDFs, reducing manual audit time by \textbf{70\%}.}
    \item {\textbf{Predictive Spend Analytics:} Developed a multivariate \textbf{Long Short-Term Memory (LSTM)} network in TensorFlow to forecast SaaS expenditure. By integrating headcount growth and historical billing cycles, the model achieved a \textbf{94\% Mean Absolute Percentage Error (MAPE)}, allowing the Finance team to optimize cash flow.}
    \item {\textbf{Intelligent License Optimization:} Engineered a \textbf{Wide \& Deep learning model} using the \textbf{tf.estimator} API to predict user "churn" from specific SaaS tools. This enabled proactive license reclamation, saving the organization over \textbf{\$400k in annual recurring costs}.}
    \item {\textbf{Shadow IT Detection:} Implemented an anomaly detection system using \textbf{Autoencoders} in TensorFlow to monitor SSO logs and API traffic. This identifies anomalous app-to-app data transfers, uncovering unauthorized "Shadow IT" with a \textbf{45\% higher detection rate} than rule-based systems.}
    \item {\textbf{Recommendation Systems:} Built a \textbf{TensorFlow Recommenders (TFRS)} engine to suggest optimal software tiers for departments. By analyzing usage patterns across the organization, the system increased internal software utility scores by \textbf{30\%}.}
    \item {\textbf{Scalable MLOps with TFX:} Orchestrated the production ML lifecycle using \textbf{TensorFlow Extended (TFX)}.Implemented automated data validation and model analysis, reducing the time-to-production for new feature sets from three weeks to four days.}
    \item {\textbf{Distributed Training \& Performance:} Leveraged \textbf{tf.distribute.MirroredStrategy} to train large-scale classification models on multi-GPU clusters, processing over \textbf{500M+ data points} from global financial feeds and usage logs.}
\end{cvitems}}
%---------------------------------------------------------

%---------------------------------------------------------

%---------------------------------------------------------

%---------------------------------------------------------

%---------------------------------------------------------
\end{cventries}
=======
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-----------------------------------------------------------------------------
\vspace{-3mm}
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\vspace{-1mm}
\begin{cventries}
%---------------------------------------------------------

\cventry
{\textbf{AI Engineer}} % Job title
{\href{https://www.zluri.com/}{Zluri, Bangalore}} % Organization
{{July. 2022 - Present}} % Date(s)
{\textbf{AI Engineer}}
{\begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Over 2 years of experience in AI/ML development with a strong focus on \textbf{NLP} and \textbf{large language models (LLMs)}.}
    \item {Deployed AI/ML models into \textbf{AWS production enviroments} using \textbf{Sagemaker and Lamda}, optimizing container orchestration to reduce inference costs by \textbf{25\%} while maintaining 99.9\% availability.}
    \item {Demonstrated excellent communication and collaboration skills within cross-functional teams.}
    \item {Debugged complex systems vulenrabilities by performing meticulous code reviews and root-cause analysis, ensuring \textbf{ 99.9\% system uptime} and zero security breaches over a 12-month period.}
    \item {Developed and deployed scalable machine learning pipelines using \textbf{Python and Sckit-learn}, automating data preprocessing and feature engineering to reduce model training time by \textbf{30\%} .}
    \item {Proficiently harnessed the power of the pandas library to extract, clean and manipulate Sales data. This process involved several crucial steps to ensure the accuracy and reliability of the information we worked with.}
    \item {Developed and consistently manage Python-based sofwtare \textbf{ Python-based sofwtare }Django and React desgined specifically for compression tasks within the swap's domain. This entails crafting efficient algorithm and processes to optimize data while adhering to industry standards.}
    \item {Additionaly, the role involves the ongoing maintenance, debugging and enhancement of the software to align with the dynamic requirements of the swaps market.}
    \item {Developed \textbf{Python scripts} that identify potential compression oppurtunities for cross-currency and inflation trades. Aiding the bank in reducing the notional value or risk exposure of financial transactions, typically derivatives or other complex instruments, by combining or netting offsetting positions.}
    \item {Contributed to the development of incremental features within the \textbf{ React framework} for the compression's platform. My role involved breaking down larger functionalities into smaller, manageable components that could be implemented iteratively. By doing so, I ensured a smooth integration of new capabilities into the existing system.}
    \item {Ideated \& implemented a development workflow for the organization using feature environments, automated testing etc. for multiple services and background jobs resulting in higher engineering productivity and faster project delivery.}
%    \item {Deployed AI/ML models into \textbf{AWS production enviroments} using \textbf{Sagemaker and Lamda}, optimizing container orchestration to reduce inference costs by \textbf{25\%} while maintaining 99.9\% availability.}
%    \item {Spearheaded the development of a domain-specific \textbf{LLM application} using \textbf{LangChain and OpenAI}, implementing \textbf{RAG (Retrieval-Augmented Generation)} with a vector database (Pinecone) to reduce hallucination rates by \textbf{35\%} in automated customer support.}
%    \item {Tools and Technologies used: TypeScript, NodeJS, Golang, Kafka, MongoDB, Postgres, AWS, CI/CD.}
%    \item {Revamped notification service with minimal impacts, reducing peak-hour message delivery latency from \textbf{2 hours} to under \textbf{1 minute}.}
%    \item {Performed cross-functional bug bashes and refactored critical legacy modules, resulting in a \textbf{33\%} drop in on-call tickets.}
%    \item {}
%    \item {Ideated \& implemented a development workflow for the organization using feature environments, automated testing etc. for multiple services and background jobs resulting in higher engineering productivity and faster project delivery}
%    \item {\textbf{Mentored junior engineers and interns} through onboarding, code reviews, and project execution.}
%    \item {Tools and Technologies used: TypeScript, NodeJS, Golang, Kafka, MongoDB, Postgres, AWS, CI/CD.}
%    \item {}
\end{cvitems}}
%---------------------------------------------------------












%---------------------------------------------------------
\end{cventries}
>>>>>>> 037d1fcd6fa27a829e7576d4d2b91a7a97d2b870
